Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-06-04 manuscript.Rmd
centering and some fixes

# select relevant variables
df <- df %>% 
  select(
    PerUn:Group, # id variables
    EA100, # emphatic accuracy (EA) for thoughts out of 100
    sex:race_text, # demographic variables
    imp1:imp16, # rapport during the interaction
    strait1:strait26, # perceivers' self-reported personality traits
    ptrait1:ptrait26, # perception of targets' personality traits
    targSR1:targSR26, # targets' self-reported personality traits
    Self1:Self120, # perceivers' self-reported continuous affect
    Part1:Part120, # perception of targets'continuous affect
    TargSR1:TargSR120, # targets' self-reported continuous affect
    as1:as13, # attachment styles
    auth1:auth12rc, # authenticity
    mask1:mask13, # masking
    ntb1:ntb10, # need to belong
    ucla1:ucla20rc, # ucla loneliness scale
    fne1:fne12, # fear of negative evaluation
    beq1:beq16, # berkeley expressivity questionnaire
    erq1:erq10, # emotion regulation (expressive suppression)
    rse1:rse10rc, # rosenberg self-esteem
    sat1:sat5, # satistaction with life
    pow1:pow8, # sense of power
    sias1:sias12, # social interaction anxiety scale
    InsecAtt:SIAPSc, # composite variables
    InformantTot, # number of informants for targets
    Extr:Trust, # composite variables for personality traits of perceivers
    itrait1:itrait26, # informant reports of targets' personality traits
    per_InsecAtt_INFmeanC:per_Trust_INFmeanC # informant reports 
  ) %>% 
  arrange(PerUn, TarUn, DyUn, Group)

@@

# composite var for rapport
df <- 
  df %>% 
  mutate(rapport = rowMeans(select(., 
                                   rapport1:rapport11,
                                   rapport12_rc:rapport15_rc),
                            na.rm = TRUE),
         # other composite variables are scaled to 0-100
         rapport = rapport - 1,
         rapport = rapport/7 * 100,
         rapport_c = scale(rapport, scale = FALSE)
         ) %>% 
  relocate(rapport, .before = informant_trait1) %>% 
  relocate(rapport_c, .before = rapport)
```

@@

## Personality (self- AND informant-reports of targets)
df_personality <-
  df %>% 
  select(perceiver_id:group_id,
         judgment_trait1:target_trait26,
         informant_trait1:informant_trait26,
         InsecAtt:Trust, -ends_with("C"), -ASMtot, -beqtot, -SIAPS)

@@

df_personality <- 
df_personality %>% 
  pivot_longer(cols = judgment_trait1:informant_trait26,
               names_to = c("trait", "item"),
               names_sep = "_",
               values_to = "rating") %>% 
  mutate(item = parse_number(item)) %>% # could not write the correct regex :(
  pivot_wider(names_from = "trait",
              values_from = "rating") %>% 
  right_join(., trait_norms, by = "item") %>% 
  mutate(self_dist = target - self_norm,
         inf_dist = informant - inf_norm,
         across(c(InsecAtt:Trust, self_norm:inf_dist), 
                scale, scale = FALSE, center = TRUE)
         )

@@

```{r}
null_trait_self <- lmer(judgment ~ 
                (1|perceiver_id) + 
                (1|target_id) + 
                (1|dyad_id) +
                (1|group_id),
              data = df_personality)
```

@@

sjPlot::tab_model(samEAC_null)

summary(samEAC_null)
```

```{r}
# thought
eaSRMdata <- import(here::here("data", "d_thought.csv"))

>>>>

# select relevant variables
df <- df %>% 
  select(
    PerUn:Group, # id variables
    EA100, # emphatic accuracy (EA) for thoughts out of 100
    sex:race_text, # demographic variables
    imp1:imp16, # rapport during the interaction
    strait1:strait26, # perceivers' self-reported personality traits
    ptrait1:ptrait26, # perception of targets' personality traits
    targSR1:targSR26, # targets' self-reported personality traits
    Self1:Self120, # perceivers' self-reported continuous affect
    Part1:Part120, # perception of targets'continuous affect
    TargSR1:TargSR120, # targets' self-reported continuous affect
    as1:as13, # attachment styles
    auth1:auth12rc, # authenticity
    mask1:mask13, # masking
    ntb1:ntb10, # need to belong
    ucla1:ucla20rc, # ucla loneliness scale
    fne1:fne12, # fear of negative evaluation
    beq1:beq16, # berkeley expressivity questionnaire
    erq1:erq10, # emotion regulation (expressive suppression)
    rse1:rse10rc, # rosenberg self-esteem
    sat1:sat5, # satistaction with life
    pow1:pow8, # sense of power
    sias1:sias12, # social interaction anxiety scale
    # composite variables
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, Open, Consc, Extr, Agree, Neurot, Intell, Trust, 
    itrait1:itrait26, # informant reports of targets' personality traits
    per_InsecAtt_INFmeanC:per_Trust_INFmeanC # informant reports 
  ) %>% 
  arrange(PerUn, TarUn, DyUn, Group)

@@

# centering
df <- 
  df %>% 
  mutate_at(list(c = ~center(.)),
            .vars = vars(InsecAtt:Trust))

# composite var for rapport
df <- 
  df %>% 
  mutate(rapport = rowMeans(select(., 
                                   rapport1:rapport11,
                                   rapport12_rc:rapport15_rc),
                            na.rm = TRUE),
         # other composite variables are scaled to 0-100
         rapport = rapport - 1,
         rapport = rapport/7 * 100,
         rapport_c = scale(rapport, scale = FALSE)
         ) %>% 
  relocate(rapport, .before = informant_trait1)
```

@@

## Personality (self- AND informant-reports of targets)
df_personality <-
  df %>% 
  select(perceiver_id:group_id,
         judgment_trait1:target_trait26,
         informant_trait1:informant_trait26,
         InsecAtt_c:rapport_c)

@@

df_personality <- # create final df for analyses
df_personality %>% 
  pivot_longer(cols = judgment_trait1:informant_trait26,
               names_to = c("trait", "item"),
               names_sep = "_",
               values_to = "rating") %>% 
  mutate(item = parse_number(item)) %>% # could not write the correct regex :(
  pivot_wider(names_from = "trait",
              values_from = "rating") %>% 
  right_join(., trait_norms, by = "item") %>% 
  mutate(self_dist = target - self_norm,
         inf_dist = informant - inf_norm
         )

## Affect
df_affect <- 
  df %>% 
  select(perceiver_id:group_id,
         target_affect1:judgment_affect120,
         InsecAtt_c:rapport_c)

affect_norms <- # average values
  df_affect %>% 
  select(target_affect1:target_affect120) %>% 
  map_df(., mean, na.rm = TRUE) %>% 
  pivot_longer(., cols = everything(),
               names_to = "second",
               names_pattern = "(\\d+)$",
               values_to = "norm") %>% 
  mutate(second = as.numeric(second))

df_affect <- 
  df_affect %>% 
  pivot_longer(cols = target_affect1:judgment_affect120,
               names_to = c("affect", "second"),
               names_sep = "_",
               values_to = "rating") %>% 
  mutate(second = parse_number(second)) %>% 
  pivot_wider(names_from = "affect",
              values_from = "rating") %>% 
  right_join(., affect_norms, by = "second") %>% 
  mutate(self_dist = target - norm,
         across(norm:self_dist, center)
         )

## Thought
df_thought <- import(here::here("data", "d_thought.csv")) %>% 
  select(PerUn, TarUn, DyUn, Group, BaselineEA:CrrctdEAnoneg) %>% 
  rename_at(vars(PerUn:Group), ~ 
              c("perceiver_id", "target_id", "dyad_id", "group_id")
             ) %>% 
  left_join(., select(df_personality, perceiver_id:group_id,
                      InsecAtt:Trust, rapport_c))

@@

```{r null models}
null_trait_self <- lmer(judgment ~ 
                (1|perceiver_id) + 
                (1|target_id) + 
                (1|dyad_id) +
                (1|group_id),
              data = df_personality)
```

@@

sjPlot::tab_model(samEAC_null, null_affect)

summary(samEAC_null)

null_affect <- lmer(judgment ~ 1 + 
                  (1|perceiver_id) + 
                  (1|target_id) + 
                  (1|dyad_id) +
                    (1|group_id), 
                data = df_affect)

```{r}
# thought
